### 2018-05-24 latex/sc18/experiments.tex
fixed label ordering for proc grid sweep exp

\begin{figure}
\renewcommand{\datafile}{data/comm_sweep_scale_pgf_10.dat}
\renewcommand{\numiterations}{10}
\begin{tikzpicture}
\begin{axis}[	
	ybar stacked,
	bar width=8pt,
	width=\columnwidth,
	height =.75\columnwidth,
	%width=9cm, height=3.85cm,
	ylabel={Time (s)}, 
	xlabel={Rank $R$},
	y label style={yshift=-.5cm},
	ymin=0,
	%symbolic x coords={D10,N10,,D20,N20,,D30,N30,,D40,N40,,D50,N50},
	symbolic x coords={81x1x1x1-10, 27x3x1x1-10,9x9x1x1-10,9x3x3x1-10,3x3x3x3-10,},
	%xtick=data,
	xticklabels={,27x3x1x1,3x3x3x3,81x1x1x1,9x3x3x1,9x9x1x1},
	legend style={at={(0.5,1.3)},anchor=north},
	legend columns=-1,
]
	\setcolors
	\addplot table[x=algo-k, y expr=(\thisrow{mttkrp}/(\minvalue*\numiterations))] {\datafile};
	\addplot table[x=algo-k, y expr=(\thisrow{mttv}/(\minvalue*\numiterations))] {\datafile};
	\addplot table[x=algo-k, y expr=((\thisrow{nnls}+\thisrow{gram})/(\minvalue*\numiterations))] {\datafile};
	\addplot table[x=algo-k, y expr=((\thisrow{allgather}+\thisrow{reducescatter})/(\minvalue*\numiterations))] {\datafile};
	\addplot table[x=algo-k, y expr=(\thisrow{allreduce}/(\minvalue*\numiterations))] {\datafile};
	\legend{PM,mTTV,NLS,Factor Comm,Gram Comm};
\end{axis}
%\labels
\end{tikzpicture}
\caption{Comm scheme for low rank $k$=10}
\label{fig:commsweep10}
\end{figure}

>>>>

\begin{figure}
\renewcommand{\datafile}{data/comm_sweep_scale_pgf_10.dat}
\renewcommand{\numiterations}{10}
\begin{tikzpicture}
\begin{axis}[	
	ybar stacked,
	bar width=8pt,
	width=\columnwidth,
	height =.75\columnwidth,
	%width=9cm, height=3.85cm,
	ylabel={Time (s)}, 
	xlabel={Processor Grid},
	y label style={yshift=-.5cm},
	ymin=0,
	%symbolic x coords={D10,N10,,D20,N20,,D30,N30,,D40,N40,,D50,N50},
	symbolic x coords={81x1x1x1-10, 27x3x1x1-10,9x9x1x1-10,9x3x3x1-10,3x3x3x3-10,},
	%xtick=data,
	xticklabels={,81x1x1x1,27x3x1x1,9x9x1x1,9x3x3x1,3x3x3x3},
	legend style={at={(0.5,1.3)},anchor=north},
	legend columns=-1,
]
	\setcolors
	\addplot table[x=algo-k, y expr=(\thisrow{mttkrp}/(\minvalue*\numiterations))] {\datafile};
	\addplot table[x=algo-k, y expr=(\thisrow{mttv}/(\minvalue*\numiterations))] {\datafile};
	\addplot table[x=algo-k, y expr=((\thisrow{nnls}+\thisrow{gram})/(\minvalue*\numiterations))] {\datafile};
	\addplot table[x=algo-k, y expr=((\thisrow{allgather}+\thisrow{reducescatter})/(\minvalue*\numiterations))] {\datafile};
	\addplot table[x=algo-k, y expr=(\thisrow{allreduce}/(\minvalue*\numiterations))] {\datafile};
	\legend{PM,mTTV,NLS,Factor Comm,Gram Comm};
\end{axis}
%\labels
\end{tikzpicture}
\caption{Time breakdown for $243\times243\times243\times243$ tensor and rank $R=10$ on 81 processors for varying processor grids.}
\label{fig:commsweep10}
\end{figure}
